Extended Data

### 2021-10-16 doc/manuscript/Dow_manuscript_Nature.Rmd
macroscopic rearrangement of methods
changed order to parallel presentation in main article

## Study sites {-#Study}

@@

## Data collection and preparation {-#Data} 
### Dendrometer bands {-#Dendrometer}

@@

### Tree rings {-#Tree} 
Dominant tree species were cored at both sites following sampling designs that covered a broad range of $DBH$.
We analyzed records for the dominant ring- and diffuse- porous species at each site (`r  EDT_species`), excluding species with other xylem architectures (*Juglans nigra* L. at SCBI, *Tsuga canadensis* (L.) Carrière at Harvard Forest)
At SCBI, cores were collected as described in @helcoski_growing_2019. 
Briefly, cores were taken from living or recently dead trees $\ge$ 10 cm $DBH$, including a randomly sampled subset of all dominant species within the ForestGEO plot [live trees in 2010-2011; @bourg_initial_2013] and trees found newly dead in annual tree mortality in 2016 and 2017 [@helcoski_growing_2019]*(If we're citing a method from the helcoski paper, do we need to do this 'briefly' section? I would remove.)*.
At Harvard Forest, ...(*Neil can write this easily, or KAT probably has the info*)
In total, we analyzed >900 cores from fourteen species at SCBI and four species at Harvard Forest (`r  EDT_species`).

## Analyses
### Determining critical temperature windows {-#Determining}

@@

>>>>

## Dendrometer bands {-#Dendrometer} 
### Study sites {-#Study}

@@

### Data collection and preparation {-#Data}

@@

### Determining critical temperature windows {-#Determining}

@@

## Tree rings {-#Tree} 
Dominant tree species were cored at both sites following sampling designs that covered a broad range of $DBH$.
We analyzed records for the dominant ring- and diffuse- porous species at each site (`r  EDT_species`), excluding species with other xylem architectures (*Juglans nigra* L. at SCBI, *Tsuga canadensis* (L.) Carrière at Harvard Forest)
At SCBI, cores were collected as described in @helcoski_growing_2019. 
Briefly, cores were taken from living or recently dead trees $\ge$ 10 cm $DBH$, including a randomly sampled subset of all dominant species within the ForestGEO plot [live trees in 2010-2011; @bourg_initial_2013] and trees found newly dead in annual tree mortality in 2016 and 2017 [@helcoski_growing_2019]*(If we're citing a method from the helcoski paper, do we need to do this 'briefly' section? I would remove.)*.
At Harvard Forest, ...(*Neil can write this easily, or KAT probably has the info*)
In total, we analyzed >900 cores from fourteen species at SCBI and four species at Harvard Forest (`r  EDT_species`).
